### 2019-12-17 Statistical Methods/05_sampling-distributions.rmd
statistical computing
statistical computing

For the values, 2, 3, 5, 6, 8, 12, 14, 18, 19, 22, 201, why would you suspect that the McKean-Schrader estiamte of the standard error of the median will be smaller than the standard error of the mean?

>>>>

For the values, 2, 3, 5, 6, 8, 12, 14, 18, 19, 22, 201, why would you suspect that the McKean-Schrader estimate of the standard error of the median will be smaller than the standard error of the mean?

_There is an outlier._

```{r, echo = T}
x <- c(2, 3, 5, 6, 8, 12, 14, 18, 19, 22, 201)

msmedse(x)

sqrt(var(x) / length(x))

### 5.24

Summarize when it would and would not be reasonable to assume that the sampling distribution of M, the sample median, is normal.

### 5.25

For the values:

59, 106, 174, 207, 219, 237, 313, 365, 485, 497, 515, 529, 557, 615, 625, 645, 973, 1065, 3215

Estimate the standard error of the 20% trimmed mean.

```{r, echo = T}
x <- c(59, 106, 174, 207, 219, 237, 313, 365, 485, 497, 515, 529, 557, 615, 625, 645, 973, 1065, 3215)
